Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2017-12-21 sections/what.tex
Added a bit of text to the hackathon section

We note that the terminology for these events is constantly evolving, and that the ``hackathon'' concept may have implicit connotations that are disfavored in some communities.
One criticism of hackathons is that they propel the ``geek'' stereotype and may present a barrier to creating an inclusive working environment, especially for individuals traditionally underrepresented in science and technology \cite{Decker2015}.
This criticism needs to be actively addressed both through participant selection (see below), and by addressing the possibility that some participants may experience an ``imposter syndrome'' within such circumstances \cite{clance1978imposter} (see supplementary material).
Also, while many industry hackathons are competitive, with teams actively competing to solve the same problems for prizes, academic hackathons, and specifically the hack weeks that we have organized are not explicitly competitive.

>>>>

The hack week model sets itself apart from other events notably in the goals that are pursued (see also Figure \ref{fig:hackspectrum}). Many industry hackathons are focused on delivering solutions to a specific problem or challenge on a very short timescale. Hack weeks are generally more open-ended than these hackathons and allow for a wider variety of outcomes and goals among participants. Within academia, the majority of venues for scientific collaboration, learning and communication fall into one of three categories: traditional conferences, summer schools, and, more recently, unconferences. All three types share elements with hack weeks, but have goals that are more narrowly defined. Traditional conferences are focused on the exchange of recent results, as well as networking. However, collaborative components are usually absent, or restricted to short time intervals (e.g.\ coffee breaks and ``hack days''). Unconferences are less structured and allow for greater input from participants, but are generally less focused on knowledge transfer and learning, but on achieving measurable outcomes. However, these outcomes are often in the form of policies, planning and white papers, whereas a hack week encourages participants to directly produce outcomes such as a paper, a visualization, or code.

Three design considerations distinguish the hack week from the summer school model: (1) hack week transfer knowledge across many levels of seniority, with participants routinely leading tutorials, in part due to the relative newness of the content and the distributed knowledge base; (2) hack weeks contain a significant amount of unstructured time, creating the conditions for improvised exchanges and project development; and (3) hack weeks intentionally priortize participant diversity because this is known to maximize the likelihood for the co-creation of learning during the event.

We note that the terminology for these events is constantly evolving, and that the ``hackathon'' concept may have implicit connotations that are disfavored in some communities.
One criticism of hackathons is that they propel the ``geek'' stereotype and may present a barrier to creating an inclusive working environment, especially for individuals traditionally underrepresented in science and technology \cite{Decker2015}.

This criticism needs to be actively addressed both through participant selection (see below), and by addressing the possibility that some participants may experience an ``imposter syndrome'' within such circumstances \cite{clance1978imposter} (see supplementary material).
%Also, while many industry hackathons are competitive, with teams actively competing to solve the same problems for prizes, academic hackathons, and specifically the hack weeks that we have organized are not explicitly competitive.
